\documentclass[11pt,a4paper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% Remove page numbers
\pagenumbering{gobble}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

% Section formatting
\titleformat{\section}
  {\normalfont\Large\bfseries\scshape}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{5pt}

% Subsection formatting
\titleformat{\subsection}
  {\normalfont\large\bfseries}{\thesubsection}{1em}{}
\titlespacing*{\subsection}{0pt}{8pt}{3pt}

% List formatting
\setlist[itemize]{leftmargin=*, itemsep=2pt, parsep=0pt, topsep=2pt}

\begin{document}

% Header
\begin{center}
    {\Huge \textbf{Ranjit Chauhan}} \\[5pt]
    {\Large Java Full Stack Developer} \\[8pt]
    8639767208 $\diamond$ ranjitchauhan20450@gmail.com $\diamond$ India $\diamond$ Open to Relocate $\diamond$ \href{https://www.linkedin.com/in/ranjit-chauhan}{LinkedIn}
\end{center}

\vspace{5pt}

% Summary Section
\section*{SUMMARY}
Java Backend Developer with 2+ years of experience at Capgemini, specializing in building scalable microservices using Spring Boot, Kafka, and SQL Server. Proven team lead of a 4-member group, delivering 35+ requirements with expertise in full-stack development, React.js, RESTful APIs, and real-time data synchronization. Top-ranked on LeetCode (13\% globally) and CodeChef (3-star), passionate about problem-solving and driving innovative, high-performance solutions.

% Experience Section
\section*{EXPERIENCE}

\textbf{SDE Intern} \hfill \textit{Mar '23 — May '23} \\
\textit{Capgemini India} \hfill \textit{Mumbai, India}
\begin{itemize}
    \item Built a web application using Java Spring Boot, Spring MVC, and JDBC with SQL Server for data handling, incorporating Object-Oriented Design principles.
    \item Developed front-end features using React.js and JavaScript frameworks for improved UI/UX.
    \item Wrote unit tests with JUnit to ensure code quality and functionality.
    \item Managed source code with GitHub, handling branching and merging.
    \item Performed data migrations and optimized SQL queries for better performance, applying data structures and algorithms for efficiency.
\end{itemize}

\vspace{5pt}

\textbf{Senior Analyst} \hfill \textit{Jul '23 — Present} \\
\textit{Capgemini India} \hfill \textit{Mumbai, India}
\begin{itemize}
    \item Serving as Team Lead for a 4-member team (including myself), successfully delivering over 35 requirements while efficiently handling and resolving post-production errors.
    \item Maintained and enhanced web applications using Spring Boot, SQL Server, and MongoDB, improving performance, reliability, and database efficiency through optimized coding and testing.
    \item Optimized SQL queries in FLARE tool integration by adding indexes and refining joins, cutting execution time by 67\% (from 90s to under 30s) and enhancing application performance for high-volume data processing.
    \item Developed new features and full-stack solutions, including an AI-powered bot using React, Java/Spring Boot backend, Python (LangChain), and FastAPI, ensuring secure and seamless user interactions.
    \item Designed RESTful APIs, implemented user authentication with Spring Security, and managed real-time data updates for robust and scalable applications.
    \item Utilized TortoiseSVN for version control and followed best practices such as clean code, design patterns to streamline development.
    \item Leveraged data structures and algorithms to enhance application performance and ensure adherence to project goals and timelines.
    \item Implemented Kafka message streaming for real-time data synchronization and event-driven microservices communication.
\end{itemize}

% Education Section
\section*{EDUCATION}

\textbf{Bachelor of Technology in Computer Science and Engineering}, Lovely Professional University (GPA: 8.37) \\
Phagwara

\textbf{Senior Secondary in Math's, Physics and Chemistry}, Army Public School (GPA: 9.45) \\
Secunderabad

\textbf{Secondary School}, Army Public School (GPA: 10) \\
Secunderabad

% Certifications Section
\section*{CERTIFICATIONS}

\textbf{Azure Fundamentals(AZ - 900)}, Microsoft \hfill \textit{Oct '23}

\textbf{AWS Cloud Technical Essentials}, Amazon Web Services (AWS) \hfill \textit{Sep '24}

\textbf{Object Oriented Programming in Java}, IBM

\textbf{Spring Framework for Java Development}, Skill Up

\textbf{Agile Software Development}, University of Minnesota \hfill \textit{Apr '24}

% Achievements Section
\section*{ACHIEVEMENTS}

\textbf{CodeChef: 3-star rating} \hfill CodeChef \\
Achieved a 3-star rating with a maximum score of 1638.

\textbf{LeetCode Weekly Contest 400} \hfill LeetCode \hfill \textit{Jan '01} \\
Achieved Rank 3,674 out of 35,706 participants.

\textbf{LeetCode: Rated 1700, ranked Top 13\% globally}

% Projects Section
\section*{PROJECTS}

\textbf{Flight Management System}, Capgemini India \hfill \textit{May '23 — May '23}
\begin{itemize}
    \item Built a flight management app with CRUD operations for scheduling and reservations.
    \item Designed and optimized database schemas using Object-Oriented Design principles.
    \item Connected Angular UI with Spring MVC and Spring Boot backend.
    \item Handled data migrations and transformations, ensuring seamless system integration testing.
\end{itemize}

\vspace{5pt}

\textbf{Lnd Automation Tool (FLARE)}, Capgemini India \hfill \textit{Aug '23}
\begin{itemize}
    \item Worked on the Lnd Automation Tool project, focusing on maintaining the current website and implementing new software solutions using Spring Boot and SQL Server.
    \item Optimized database operations and enhanced application performance through efficient coding, leveraging data structures and algorithms.
    \item Managed source code and project versions using TortoiseSVN, facilitating smooth development and deployment processes.
    \item Followed best coding practices, including clean code principles, code reviews, and adherence to design patterns and continuous integration.
\end{itemize}

\vspace{5pt}

\textbf{FLARE AI Bot}, Capgemini India \hfill \textit{Dec '24 — May '25}
\begin{itemize}
    \item Developed a full-stack AI-powered web application to answer queries related to FLARE tool processes, integrating React frontend with Java Spring Boot backend for seamless user interactions.
    \item Built and optimized a MongoDB database for storing and managing legal queries and responses, ensuring efficient data retrieval and real-time updates with JSON.
    \item Integrated LangChain with Python to implement a conversational AI model capable of providing query resolution using FastAPI for chat service.
    \item Designed RESTful APIs and implemented user authentication with Spring Security to ensure secure interactions and privacy of sensitive legal data.
    \item Improved system performance by optimizing backend queries and ensured scalable handling of high user volumes through performance analysis.
\end{itemize}

% Skills Section
\section*{SKILLS}

\textbf{Relevant Skills} \\
Microservices, Object-Oriented Design, Kafka, Maven, REST, Computer Networks, Operating System, Reactive Programming, Data Structures and Algorithms, Caching

\textbf{Design Patterns} \\
Strategy, Builder, Proxy, Chain of Responsibility, Factory, Observer, NULL Object

\textbf{Programming} \\
Java, SQL, C\#, JavaScript, HTML, CSS

\textbf{Frameworks} \\
Spring Boot, JDBC, Hibernate, React.js, .NET Core, .NET MVC, Node.js, Kafka, Junit5

\textbf{Database Management} \\
SQL Server, MongoDB

\textbf{Version Control} \\
TortoiseSVN, Git

\textbf{Cloud Technologies} \\
Azure Fundamentals, AWS Fundamentals, GitHub Actions, CI/CD Pipelines

\textbf{Tools} \\
Docker, Visual Studio Code, Visual Studio, IntelliJ IDEA

\end{document}